Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-03 paper.qmd
Adding code for running with labels
Robust stats application fixed with providing mu value

set.seed(129)
animate_xy(X, 
           guided_anomaly_tour(anomaly_index(),
                               ellipse=as.matrix(Sigma),
                               ellc = size_weather), 
           ellipse=as.matrix(Sigma), ellc = size_weather,
           axes="off", col = as.factor(cluster_labels),
           palette = "Plasma", half_range = 5,
           center = FALSE, rescale = FALSE)

>>>>

set.seed(22)
animate_xy(X, 
           guided_anomaly_tour(anomaly_index(),
                               ellipse=as.matrix(Sigma),
                               ellc = size_weather,
                               ellmu = mu), 
           ellipse=as.matrix(Sigma), ellc = size_weather,
           ellmu = mu,
           axes="off", col = as.factor(cluster_labels),
           palette = "Purple-Yellow",
           center = FALSE, rescale = FALSE)
